Manuscript_Github_Pchabaudi_calculateTPM

### 2022-07-21 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_calculateTPM.Rmd
Change name of twentyfour_ct_comb to chab_tpm.df and check TPM all add to 1e6

```{r calc_tpm}
#Read in the count data and remove one sample which is unknown and had no description.
chab_count_table <- read.csv('data/tl19-07_twentyfour_counts_samples.csv') %>% 
  select(-rMT_Unknown)
#Calculate the TPM
twentyfour_ct_comb <- tpm(count_data = chab_count_table, 
                          lengths = chabaudi_transcript_lengths)
```

@@

twentyfour_tpm_nopseudo <- twentyfour_ct_comb %>% 
  filter(!Geneid %in% 'PCHAS_0420800')

@@

#Setting the re-scaled version as the default from now on
#Setting twentyfour_tpm_ct core dataset - removed pseudogene and re-scaled
twentyfour_ct_comb <- twentyfour_tpm_rescale_nopseudo
```

@@

twentyfour_ct_comb <- rename_with(twentyfour_ct_comb, 
                                  ~ str_extract(.x,pattern = '(?<=rMT_).+'),
                                  matches('rMT'))

twentyfour_rMT_avg <- melt(twentyfour_ct_comb, 
                           variable.name = 'sample',
                           value.name = 'tpm') %>% 
  mutate(stage = str_extract(sample, pattern = '.+(?=_[[:digit:]])')) %>% 
  group_by(Geneid, stage) %>% 
  summarise(mean_tpm = mean(tpm)) %>% 
  dcast(Geneid ~ stage)
```

>>>>

```{r calc_tpm}
#Read in the count data and remove one sample which is unknown and had no description.
chab_count_table <- read.csv('data/tl19-07_twentyfour_counts_samples.csv') %>% 
  select(-rMT_Unknown)
#Calculate the TPM
chab_tpm.df <- tpm(count_data = chab_count_table, 
                          lengths = chabaudi_transcript_lengths)

#Do they all sum to 1e6? Note that all.equal allows for a tiny bit of difference which is okay.
all.equal(apply(twentyfour_ct_comb[-1], 2, sum), 
          rep(1e6, times = dim(twentyfour_ct_comb[-1])[2]), 
          check.names = FALSE)
```

@@

twentyfour_tpm_nopseudo <- chab_tpm.df %>% 
  filter(!Geneid %in% 'PCHAS_0420800')

@@

#Setting the re-scaled version as the default from now on
#Setting twentyfour_tpm_ct core dataset - removed pseudogene and re-scaled
chab_tpm.df <- twentyfour_tpm_rescale_nopseudo
```

@@

chab_tpm.df <- rename_with(chab_tpm.df, 
                                  ~ str_extract(.x,pattern = '(?<=rMT_).+'),
                                  matches('rMT'))

twentyfour_rMT_avg <- melt(chab_tpm.df, 
                           variable.name = 'sample',
                           value.name = 'tpm') %>% 
  mutate(stage = str_extract(sample, pattern = '.+(?=_[[:digit:]])')) %>% 
  group_by(Geneid, stage) %>% 
  summarise(mean_tpm = mean(tpm)) %>% 
  dcast(Geneid ~ stage)
```
